---
title: "R Notebook"
output:
  html_document:
    df_print: paged
  pdf_document: default
---

##Part 1

Here we generate our data

```{r}
library("BSDA")
library("EnvStats")
n <- 38
f <- function(k, ...) {
  a_k = (k*log(k^2*n + pi))%%1
  return (a_k)
}

a.data <- sapply(1:150, f)
x_k <- qnorm(a.data[1:100])
y_l <- qnorm(a.data[101:150])

x_k

```



**Problem 1**

Since we don't have variance we have to use t-test. $C_{0,05} = x \in R^{100}: T(x) \leq t^{99}_{0,05}$

```{r}
library("BSDA")
library("EnvStats")
t.test(x_k, alternative = "l")
```

Here we can see that p-value = 0.646, so it is bigger than 0.05. It means that we have to accept $H_0$.


**Problem 2**

Variance is known and we want to test mean. In such case we have to use z-test.

```{r}
library("BSDA")
library("EnvStats")
z.test(x_k, y_l, sigma.x = sqrt(2), sigma.y = sqrt(2), mu = 0, alternative = "t")
```

Here we can see that p-value = 0.9449, so it is bigger than 0.05. It means that we have to accept $H_0$.

**Problem 3**

We want to test variance so we will use chi-squared test.

```{r}
library("BSDA")
library("EnvStats")
varTest(x_k)
```


Here we can see that p-value = 0.4028, so it is bigger than 0.05. It means that we have to accept $H_0$.

**Problem 4**

We don't know mean so we will use f-test to compare variances.

```{r}
library("BSDA")
library("EnvStats")
var.test(x_k, y_l, alternative = "g")
```

Here we can see that p-value = 0.1328, so it is bigger than 0.05. It means that we have to accept $H_0$.


##Part 2

**Problem 5**

Let's generate our data

```{r}
n <- 38
q <- function(k, ...) {
  x_k = 10 * (1 + cos(k*n))
}

p <- function(k, ...) {
  y_k = sin(n + cos(k^2)) + cos(n + sin(k^2)/k) * (1 + sin(k^2)/k) * q(k)
}

x.data <- sapply(1:50, q)
y.data <- sapply(1:50, p)
```


And now we will get the summary about our model
```{r}
lm.f <- lm(x.data ~ y.data)

summary(lm.f)

```
Here is also estimate of parameters a b, and $\sigma^2$

```{r}
coef(lm.f)
```

Our confidence interval

```{r}
predict(lm.f, interval = 'confidence')

```
